### 2015-11-04 CVPR16/Source/experiments.tex
fixed the plot and added a table for association results.

Figure~\ref{fig:assoc-occ-results} presents the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset. From the results, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. Both RAS and BM often have the highest errors and hence the highest mean errors on all sets of input point tracks.

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of point tracks. The
    numbers on y-axis represent the data sequence number in KITTI dataset. The
    first set of bars in each plot correspond to the mean across all sequences.
    The error is in terms of average fraction of foreground points incorrectly
    associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}

>>>>

Table~\ref{tab:meanAssoc} and Figure~\ref{fig:assoc-occ-results} present the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset. From the results, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. Both RAS and BM often have the highest errors and hence the highest mean errors on all sets of input point tracks.

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of point tracks. The
    numbers on y-axis represent the data sequence number in KITTI dataset. The
    first set of bars in each plot correspond to the mean across all sequences.
    The error is in terms of average fraction of foreground points incorrectly
    associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}
\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 37.8 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 29.3 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 21.5 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 16.4 \\
  \bottomrule
\end{tabular}
\caption{Mean association experiment results in error percentage calculated as percentage of points wrongly associated.}
\label{tab:meanAssoc}
\end{table}
